---
title: "Basline Machine Learning For Kaggle"
output: html_document
date: "2023-11-12"
---

## Load Data

```{r}
library(tidyverse)
library(randomForest)
library(randomForestExplainer)
library(neuralnet)
library(keras)
library(dummy)
```

## Load Data

```{r}
# Load the training dataset
training <- read.csv("training.csv")
testing <- read.csv("testing.csv")
tes <- read.csv("submission20231129132211.csv")
```

## Basic Preprocessing

```{r}
# Basic Preprocessing: Remove rows with missing values
training <- na.omit(training)
training <- training[!(training$market=="") | (training$area==""), ]
```

```{r}
#for (i in 0:27) {
  #col_name <- paste0("X.", i)
  #condition <- as.numeric(training[[col_name]]) > 47000
  #training[[col_name]][condition] <- gsub("0+$", "", training[[col_name]][condition], perl = TRUE)
  #training[[col_name]] <- as.numeric(training[[col_name]])
#}

#for (i in 0:27) {
  #col_name <- paste0("X.", i)
  #condition <- as.numeric(testing[[col_name]]) > 47000
  #testing[[col_name]][condition] <- gsub("0+$", "", testing[[col_name]][condition], perl = TRUE)
  #testing[[col_name]] <- as.numeric(testing[[col_name]])
#}
```

```{r}
#for (i in 0:27) {
  #plot(training[[paste0("X.", i)]], training$y, 
  #     type = "o", col = "blue", pch = 16,
 #      main = paste0("Plot ", i), xlab = paste0("X.", i), ylab = "y")
#}
```


```{r}
# Split the data into training and testing sets
set.seed(114)  # Set seed for reproducibility
split_ratio <- 0.8  # 80% training, 20% testing
num_rows <- nrow(training)

train_indices <- sample(1:num_rows, size = round(split_ratio * num_rows))
train_data <- training[train_indices, ]
test_data <- training[-train_indices, ]
```

## Training and Evaluating Model

```{r}
# Assume 'categorical_column1' and 'categorical_column2' are the names of your categorical columns
categorical_columns <- c('area', 'market')

# One-hot encode categorical columns
train_data <- cbind(train_data, model.matrix(~ ., data = train_data[, categorical_columns]))
test_data <- cbind(test_data, model.matrix(~ ., data = test_data[, categorical_columns]))

# Define the target variable column name (replace "target_column" with your actual column name)
target_column <- "Y"

# Convert target column to numeric
train_data$target_column <- as.numeric(train_data$target_column)
test_data$target_column <- as.numeric(test_data$target_column)

# Create formula for neural network
formula_string <- paste(target_column, "~", paste(names(train_data)[!names(train_data) %in% c(target_column, categorical_columns)], collapse = "+"))

# Define the neural network formula explicitly
nn_formula <- as.formula(formula_string)

# Create and train the neural network model
nn_model <- neuralnet(nn_formula, data = train_data, hidden = c(5, 2), linear.output = TRUE)

# Make predictions on the test set
predictions <- predict(nn_model, newdata = test_data)

# Convert predictions to binary values
predictions <- ifelse(predictions > 0.5, 1, 0)

# Evaluate the model (replace "actual_values" with the actual target values in your test set)
accuracy <- mean(predictions == test_data$target_column)
cat("Accuracy:", accuracy, "\n")
```


# Training the linear regression model using all predictors (Y ~ .)

# Create and train the Random Forest model
# rf_model <- randomForest(formula = as.formula("Y ~ ."), data = train_data, ntree = 1000)

nn_model = neuralnet("Y ~ .", data=train_data, hidden=c(4,2),linear.output = FALSE)

#rf_explainer <- randomForestExplainer::explain_rf(rf_model, data = as.matrix(train_data[, -which(names(train_data) == Y)]), y = train_data[[Y]])

# Make predictions on the test set
predictions <- predict(nn_model, newdata = test_data)

# Evaluate the model using Mean Squared Error (MSE)
mse <- mean((predictions - test_data$Y)^2)
print(paste("Mean Squared Error:", mse))


## Kaggle Subsmission

```{r}
# Load the Kaggle testing dataset
kaggle.test  <- read.csv("testing.csv") 

# Make predictions on the Kaggle testing set
kaggle.test.predictions <- predict(rf_model, newdata = kaggle.test)

# Create a submission data frame with 'index' and 'Y' columns
submission <- cbind(kaggle.test$index, kaggle.test.predictions)
colnames(submission) <- c("index", "Y")

# Generate a unique filename based on the current timestamp
filename = paste("submission",format(Sys.time(), "%Y%m%d%H%M%S"),".csv", sep="")

# Save the submission data frame to a CSV file
write.csv(submission, filename, row.names = FALSE)
```

